Ground state energy of quantum dots using the coupled cluster method

### 2018-10-13 project_2/article/article.tex
Fix an index error in amplitude equations

            Now comes the rather tedious task of evaluating all the terms that
            arises from inserting \autoref{eq:normal_order_expansion} into
            \autoref{eq:doubles_amplitude_1}. This can be done by applying
            Wick's generalised theorem, but the task is a daunting and streneous
            one. A few example computations of how this can be done is included
            in Appendix \ref{app:wick_on_amplitude}. Instead of doing it in this
            manner, we employ the second quantization library from SymPy
            \footnote{This is also more in the spirit of this project, as
            it is within the realm of \emph{Computational} Physics.}.  The CCD
            amplitude equation, from SymPy\footnote{Note that this is one of
            many ways to write the amplitude equation as the ordering of the
            indices can change drastically for every run of the SymPy-script.},
            is
            \begin{equation}
                \begin{aligned}
                    0 &= u^{ab}_{ij} + f^b_c t^{ac}_{ij}P(ab)
                    - f^k_jt^{ab}_{ik}P(ij)
                    \\
                    &\qquad
                    + \frac{1}{4}t^{cd}_{ij} t^{ab}_{mn} u^{mn}_{cd}
                    + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd}
                    \\
                    &\qquad
                    + \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{mn}_{cd} P(ij)
                    - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab)
                    \\
                    &\qquad
                    + t^{ac}_{im} t^{bd}_{jn} u^{mn}_{cd} P(ij)
                    + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij)
                    \\
                    &\qquad
                    - \frac{1}{2}t^{ab}_{im} u^{mn}_{jn}.
                    \label{eq:CCD_amp_1}
                \end{aligned}
            \end{equation}
            Here $P(ij)$ is an exchange operator which interchanges two
            particles with indices $i$ and $j$.

@@

        \subsubsection{Intermediate computations}
            Looking closely at the tensors in \autoref{eq:CCD_amp_1} one might
            come to realize that many of the terms share a common structure.
            This warrants the search for an algebraic transformation of the
            amplitude equation that has the potential to reduce the amount of
            floating point operations needed to compute it. As it turns out,
            such terms exist and they will decrease the computing time necessary
            by two orders of magnitude for the price of higher storage costs.
            We will define the following "intermediates"\footnote{Note that are
            more than one way of defining the intermediates.},
            \begin{align}
                \label{eq:intermediate1}
                \chi^{ab}_{cd}
                &= \frac{1}{4}t^{ab}_{mn} u^{mn}_{cd}
                + \frac{1}{2}u^{ab}_{cd} \\
                \label{eq:intermediate2}
                \chi^n_j &= \frac{1}{2}t^{cd}_{jm} u^{mn}_{cd} \\
                \label{eq:intermediate3}
                \chi^a_d &= \frac{1}{2} t^{ac}_{nm} u^{nm}_{cd} \\
                \label{eq:intermediate4}
                \chi^{bm}_{jc}
                &= u^{bm}_{jc} + \frac{1}{2}t^{bd}_{jn}u^{mn}_{cd}
            \end{align}
            See Appendix \ref{app:intermediates} for the derivation.  These
            intermediate structures will allow us to rewrite
            \autoref{eq:CCD_amp_1} to,
            \begin{equation}
                \begin{aligned}
                    0 &= u^{ab}_{ij} + f^b_c t^{ac}_{ij}P(ab)
                    - f^k_jt^{ab}_{ik}P(ij) \\
                    &\qquad
                    + t^{cd}_{ij}\chi^{ab}_{cd} + t^{ab}_{in}\chi^n_jP(ij)
                    - t^{bd}_{ij}\chi^a_dP(ab) \\
                    &\qquad
                    + t^{ac}_{im}\chi^{bm}_{jc}P(ab)P(ij)
                    + \frac{1}{2}t^{ab}_{im}u^{mn}_{jn}.
                \end{aligned}
            \end{equation}
            Doing this reduces the number of FLOPS from $\mathcal{O}(M^4N^4)$
            for the heaviest contraction, i.e., the contraction
            \begin{align}
                g(f, u, t) \gets
                \frac{1}{4}t^{cd}_{ij}t^{ab}_{nm}u^{mn}_{cd},
            \end{align}
            to $\mathcal{O}(M^4N^2)$ when using the largest intermediate to do
            the contraction
            \begin{align}
                g(f, u, t) \gets t^{cd}_{ij}\chi^{ab}_{cd},
            \end{align}
            for the price of storing $M^4$ more matrix elements and
            pre-computing the intermediate.

>>>>

            Now comes the rather tedious task of evaluating all the terms that
            arises from inserting \autoref{eq:normal_order_expansion} into
            \autoref{eq:doubles_amplitude_1}. This can be done by applying
            Wick's generalised theorem, but the task is a daunting and streneous
            one. A few example computations of how this can be done is included
            in Appendix \ref{app:wick_on_amplitude}. Instead of doing it in this
            manner, we employ the second quantization library from SymPy
            \footnote{This is also more in the spirit of this project, as
            it is within the realm of \emph{Computational} Physics.}.  The CCD
            amplitude equation, from SymPy\footnote{Note that this is one of
            many ways to write the amplitude equation as the ordering of the
            indices can change drastically for every run of the SymPy-script.},
            is
            \begin{equation}
                \begin{aligned}
                    0 &= u^{ab}_{ij} + f^b_c t^{ac}_{ij}P(ab)
                    - f^k_jt^{ab}_{ik}P(ij)
                    \\
                    &\qquad
                    + \frac{1}{4}t^{cd}_{ij} t^{ab}_{mn} u^{mn}_{cd}
                    + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd}
                    \\
                    &\qquad
                    + \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{mn}_{cd} P(ij)
                    - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab)
                    \\
                    &\qquad
                    + t^{ac}_{im} t^{bd}_{jn} u^{mn}_{cd} P(ij)
                    + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij)
                    \\
                    &\qquad
                    + \frac{1}{2}t^{ab}_{mn} u^{mn}_{ij}.
                    \label{eq:CCD_amp_1}
                \end{aligned}
            \end{equation}
            Here $P(ij)$ is an exchange operator which interchanges two
            particles with indices $i$ and $j$.

@@

        \subsubsection{Intermediate computations}
            Looking closely at the tensors in \autoref{eq:CCD_amp_1} one might
            come to realize that many of the terms share a common structure.
            This warrants the search for an algebraic transformation of the
            amplitude equation that has the potential to reduce the amount of
            floating point operations needed to compute it. As it turns out,
            such terms exist and they will decrease the computing time necessary
            by two orders of magnitude for the price of higher storage costs.
            We will define the following "intermediates"\footnote{Note that are
            more than one way of defining the intermediates.},
            \begin{align}
                \label{eq:intermediate1}
                \chi^{ab}_{cd}
                &= \frac{1}{4}t^{ab}_{mn} u^{mn}_{cd}
                + \frac{1}{2}u^{ab}_{cd} \\
                \label{eq:intermediate2}
                \chi^n_j &= \frac{1}{2}t^{cd}_{jm} u^{mn}_{cd} \\
                \label{eq:intermediate3}
                \chi^a_d &= \frac{1}{2} t^{ac}_{nm} u^{nm}_{cd} \\
                \label{eq:intermediate4}
                \chi^{bm}_{jc}
                &= u^{bm}_{jc} + \frac{1}{2}t^{bd}_{jn}u^{mn}_{cd}
            \end{align}
            See Appendix \ref{app:intermediates} for the derivation.  These
            intermediate structures will allow us to rewrite
            \autoref{eq:CCD_amp_1} to,
            \begin{equation}
                \begin{aligned}
                    0 &= u^{ab}_{ij} + f^b_c t^{ac}_{ij}P(ab)
                    - f^k_jt^{ab}_{ik}P(ij) \\
                    &\qquad
                    + t^{cd}_{ij}\chi^{ab}_{cd} + t^{ab}_{in}\chi^n_jP(ij)
                    - t^{bd}_{ij}\chi^a_dP(ab) \\
                    &\qquad
                    + t^{ac}_{im}\chi^{bm}_{jc}P(ab)P(ij)
                    + \frac{1}{2}t^{ab}_{mn}u^{mn}_{ij}.
                \end{aligned}
            \end{equation}
            Doing this reduces the number of FLOPS from $\mathcal{O}(M^4N^4)$
            for the heaviest contraction, i.e., the contraction
            \begin{align}
                g(f, u, t) \gets
                \frac{1}{4}t^{cd}_{ij}t^{ab}_{nm}u^{mn}_{cd},
            \end{align}
            to $\mathcal{O}(M^4N^2)$ when using the largest intermediate to do
            the contraction
            \begin{align}
                g(f, u, t) \gets t^{cd}_{ij}\chi^{ab}_{cd},
            \end{align}
            for the price of storing $M^4$ more matrix elements and
            pre-computing the intermediate.
